A Spiking Independent Accumulator Model for Winner-Take-All

### 2017-01-24 doc/paper/paper.tex
Fix misplaced figure label commands.

\begin{figure}
    \centering
    \includegraphics{figures/usher-mcclelland}
    \caption{ \label{fig:usher-mcclelland}
        Example time course of the state variables in the LCA network with three choices.
        The vector of inputs is given by $(0.8, 0.7, 0.6)$.
    }
\end{figure}

@@

%Instead of controlling the threshold $\vartheta$, it is more convenient to keep $\vartheta$ fixed and scale the input with the $\lambda$ parameter -- mathematically this is equivalent.
% ^ this isn't quite equivalent. you also need to multiply the Heaviside by lambda in order to keep the feedback having the same relative magnitude
% it would be equivalent to scale \tau_1 inversely with \lambda
% also I think this point isn't too important?
%As the LCA model does not have a threshold parameter, we do not introduce the input scaling $\lambda$ in that model.
\begin{figure}
    \centering
    \includegraphics{figures/indacc}
    \caption{ \label{fig:indacc}
        Example time course of the state variables $x_i$ and decoded output $\bar{x}_i$ in the IA network with three choices.
        The vector of inputs is given by (0.8, 0.7, 0.6).
        \todo{Put next to (or below) first figure.}
    }
\end{figure}

@@

\section{Results}
We find that the ability to reach a clear decision depends on the magnitude of the highest input for both networks.
This is not surprising.
In the LCA network the output magnitude will be determined by the input magnitude of the largest input.
As such the largest input needs to be above 0.15 to fulfil the requirements.
For the IA network, the input has to be large enough to reach the integration threshold within the time limit.
By increasing the input scaling $\lambda$, or the time limit, one could get a clear decision for smaller inputs within the time limit.
We further find that the IA network is independent of the input noise and target separation for all tested parameters.\todo{but how does it do? can you put a single line on figure 3 to show it, so we can see the comparison to LCA? something visual would be good.}
This is not the case for the LCA network where the fraction of trials without a clear decision increases with noise and smaller target separation (see Fig.~\ref{fig:decisions}).
\begin{figure}
    \centering
    \includegraphics{figures/decisions}
    \caption{ \label{fig:decisions}
        Fraction of trials with a clear decision for different input noise standard deviations $\sigma$ and target separations $s$ for the LCA network.
        Error bars denote bootstrapped 95\% confidence intervals.
        The grey horizontal line shows the optimum.
    }
\end{figure}

However, when considering the correctness of the decisions (see Fig.~\ref{fig:correct}) the LCA network does better with the default parameters.
We can alleviate that difference to some degree by reducing the input scaling to $\lambda = 0.2$, but the IA network still performs worse for some combinations of input noise and target separation when staying below the time limit.
This is part due in part to a systematic bias for certain choices introduced in the second layer of the IA network.
In the NEF the neuron gain and bias parameters are usually picked from random distributions.
As such the layer 2 populations will become active at slightly different thresholds.
By using identical layer 2 populations, i.e.~identical gain and bias parameters for each population, this bias can be eliminated and the IA network performs better than the LCA network in most instances.
\todo{label fig 4 with a, b,c d and refer to those letters in the discussion above}
\begin{figure*}
    \centering
    \includegraphics{figures/correct}
    \caption{ \label{fig:correct}
        Fraction of correct trials for different input noise standard deviations $\sigma$, target separations $s$, and models.  
        Error bars denote bootstrapped 95\% confidence intervals.
        The grey horizontal line shows the optimum.
    }
\end{figure*}

The time required to reach a decision in the LCA network depends mostly on the target separation and the amount of noise on the input (see Fig.~\ref{fig:time}\todo{put a and b here too and reference them in the discussion}), the magnitude of the largest input is of minor influence.
Also, the confidence intervals indicate a larger variance in the decision times with less target separation and more input noise.
In contrast to that, in the IA network the scaled magnitude of the largest input is the most important factor.
Depending on this magnitude the network can either be faster or slower than the LCA network, but it will need more time to achieve the same fraction of correct responses.
There is also a slight influence of target separation and input noise with an interaction of these two parameters.
\begin{figure*}
    \centering
    \includegraphics{figures/time}
    \caption{ \label{fig:time}
        Mean decision times for different input noise standard deviations $\sigma$ and target separations $s$ for the LCA and IA networks.
        For the IA network $u = 0.2$ is shown which shows the interaction of target separation and input noise most clearly.
        Error bars denote bootstrapped 95\% confidence intervals.
        The grey horizontal lines show the optimum.
    }
\end{figure*}

The output of the IA network matches almost perfectly the specifications of producing an output of one for the winner and zero for all other choices \todo{a line on the LCA graph would help here too}.
This is not the case for the LCA network (see Fig.~\ref{fig:error}\todo{again a and b}).
For small target separations, the output of the winner will stay below $u$ and this will get worse with increased noise.
Furthermore, the LCA network will have residual outputs of losing choices under noisy conditions and with small target separations.
\begin{figure*}
    \centering
    \includegraphics{figures/error}
    \caption{ \label{fig:error}
        Error on outputs for different input noise standard deviations $\sigma$ and target separations $s$ for the LCA network.
        Error bars denote bootstrapped 95\% confidence intervals.
        The grey horizontal lines show the optimum.
    }
\end{figure*}

Finally, looking at the transient responses both models might produce outputs of losing choices (see Fig.~\ref{fig:transient}).
For the LCA network these increase with noise on the input and, for small target separation, can approach the final output of the winning choices.
For the IA network, transient outputs are smaller in noisy conditions, but can be higher than for the LCA network in less noisy conditions.
The magnitude of such transient responses is reduced by decreasing the input scaling.
\begin{figure*}
    \centering
    \includegraphics{figures/transient}
    \caption{ \label{fig:transient}
        Highest output of losing choices for different input noise standard deviations $\sigma$ and target separations $s$ for the LCA and IA networks.
        Error bars denote bootstrapped 95\% confidence intervals.
        The grey horizontal lines show the optimum.
    }
\end{figure*}

>>>>

\begin{figure}
    \centering
    \includegraphics{figures/usher-mcclelland}
    \caption{
        Example time course of the state variables in the LCA network with three choices.
        The vector of inputs is given by $(0.8, 0.7, 0.6)$.
    }\label{fig:usher-mcclelland}
\end{figure}

@@

%Instead of controlling the threshold $\vartheta$, it is more convenient to keep $\vartheta$ fixed and scale the input with the $\lambda$ parameter -- mathematically this is equivalent.
% ^ this isn't quite equivalent. you also need to multiply the Heaviside by lambda in order to keep the feedback having the same relative magnitude
% it would be equivalent to scale \tau_1 inversely with \lambda
% also I think this point isn't too important?
%As the LCA model does not have a threshold parameter, we do not introduce the input scaling $\lambda$ in that model.
\begin{figure}
    \centering
    \includegraphics{figures/indacc}
    \caption{
        Example time course of the state variables $x_i$ and decoded output $\bar{x}_i$ in the IA network with three choices.
        The vector of inputs is given by (0.8, 0.7, 0.6).
        \todo{Put next to (or below) first figure.}
    }\label{fig:indacc}
\end{figure}

@@

\section{Results}
We find that the ability to reach a clear decision depends on the magnitude of the highest input for both networks.
This is not surprising.
In the LCA network the output magnitude will be determined by the input magnitude of the largest input.
As such the largest input needs to be above 0.15 to fulfil the requirements.
For the IA network, the input has to be large enough to reach the integration threshold within the time limit.
By increasing the input scaling $\lambda$, or the time limit, one could get a clear decision for smaller inputs within the time limit.
We further find that the IA network is independent of the input noise and target separation for all tested parameters.\todo{but how does it do? can you put a single line on figure 3 to show it, so we can see the comparison to LCA? something visual would be good.}
This is not the case for the LCA network where the fraction of trials without a clear decision increases with noise and smaller target separation (see Fig.~\ref{fig:decisions}).
\begin{figure}
    \centering
    \includegraphics{figures/decisions}
    \caption{
        Fraction of trials with a clear decision for different input noise standard deviations $\sigma$ and target separations $s$ for the LCA network.
        Error bars denote bootstrapped 95\% confidence intervals.
        The grey horizontal line shows the optimum.
    }\label{fig:decisions}
\end{figure}

However, when considering the correctness of the decisions (see Fig.~\ref{fig:correct}) the LCA network does better with the default parameters.
We can alleviate that difference to some degree by reducing the input scaling to $\lambda = 0.2$, but the IA network still performs worse for some combinations of input noise and target separation when staying below the time limit.
This is part due in part to a systematic bias for certain choices introduced in the second layer of the IA network.
In the NEF the neuron gain and bias parameters are usually picked from random distributions.
As such the layer 2 populations will become active at slightly different thresholds.
By using identical layer 2 populations, i.e.~identical gain and bias parameters for each population, this bias can be eliminated and the IA network performs better than the LCA network in most instances.
\todo{label fig 4 with a, b,c d and refer to those letters in the discussion above}
\begin{figure*}
    \centering
    \includegraphics{figures/correct}
    \caption{
        Fraction of correct trials for different input noise standard deviations $\sigma$, target separations $s$, and models.  
        Error bars denote bootstrapped 95\% confidence intervals.
        The grey horizontal line shows the optimum.
    }\label{fig:correct}
\end{figure*}

The time required to reach a decision in the LCA network depends mostly on the target separation and the amount of noise on the input (see Fig.~\ref{fig:time}\todo{put a and b here too and reference them in the discussion}), the magnitude of the largest input is of minor influence.
Also, the confidence intervals indicate a larger variance in the decision times with less target separation and more input noise.
In contrast to that, in the IA network the scaled magnitude of the largest input is the most important factor.
Depending on this magnitude the network can either be faster or slower than the LCA network, but it will need more time to achieve the same fraction of correct responses.
There is also a slight influence of target separation and input noise with an interaction of these two parameters.
\begin{figure*}
    \centering
    \includegraphics{figures/time}
    \caption{
        Mean decision times for different input noise standard deviations $\sigma$ and target separations $s$ for the LCA and IA networks.
        For the IA network $u = 0.2$ is shown which shows the interaction of target separation and input noise most clearly.
        Error bars denote bootstrapped 95\% confidence intervals.
        The grey horizontal lines show the optimum.
    }\label{fig:time}
\end{figure*}

The output of the IA network matches almost perfectly the specifications of producing an output of one for the winner and zero for all other choices \todo{a line on the LCA graph would help here too}.
This is not the case for the LCA network (see Fig.~\ref{fig:error}\todo{again a and b}).
For small target separations, the output of the winner will stay below $u$ and this will get worse with increased noise.
Furthermore, the LCA network will have residual outputs of losing choices under noisy conditions and with small target separations.
\begin{figure*}
    \centering
    \includegraphics{figures/error}
    \caption{
        Error on outputs for different input noise standard deviations $\sigma$ and target separations $s$ for the LCA network.
        Error bars denote bootstrapped 95\% confidence intervals.
        The grey horizontal lines show the optimum.
    }\label{fig:error}
\end{figure*}

Finally, looking at the transient responses both models might produce outputs of losing choices (see Fig.~\ref{fig:transient}).
For the LCA network these increase with noise on the input and, for small target separation, can approach the final output of the winning choices.
For the IA network, transient outputs are smaller in noisy conditions, but can be higher than for the LCA network in less noisy conditions.
The magnitude of such transient responses is reduced by decreasing the input scaling.
\begin{figure*}
    \centering
    \includegraphics{figures/transient}
    \caption{
        Highest output of losing choices for different input noise standard deviations $\sigma$ and target separations $s$ for the LCA and IA networks.
        Error bars denote bootstrapped 95\% confidence intervals.
        The grey horizontal lines show the optimum.
    }\label{fig:transient}
\end{figure*}
